---
title: "Supplement for Lecture 14: Assessing a Multiple Regression Model"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
#This code chunk is for modifying the global options and for loading required R packages
knitr::opts_chunk$set(echo = TRUE)
options(scipen=999) #Prevents the use of scientific notation
library(rmarkdown)
library(tinytex)
library(knitr)
library(readr)
library(mosaic) 
library(AER)

source("https://raw.githubusercontent.com/JA-McLean/STOR455/master/scripts/anova455.R") #For modified ANOVA table from Dr. McLean
```

# Load and Clean Data 

Variables of Interest in `fatal`
- *adj_fatal* = Number of Vehicle Fatalities Per 1,000 People
- *youngdrivers* = Percent of Drivers 15 - 24
- *year* = Year
- *unemp* = Unemployment Rate
- *beertax* = Tax on Case of Beer
- *miles* = Average Miles Per Driver


```{r, message=FALSE}
data("Fatalities") # Load Data

fatal = Fatalities[,c("fatal","pop","youngdrivers","year",
                      "unemp","beertax","miles")]
fatal$adj_fatal = (fatal$fatal/fatal$pop)*1000
fatal$youngdrivers=fatal$youngdrivers*100
fatal$year = as.numeric(fatal$year) #Need to Convert to Numeric Variable (Currently a Factor Variable)

fatal$fatal=NULL
fatal$pop=NULL

#Rearrange Variables (Put "Y" variable at Beginning)
fatal=fatal[,c(6,1:5)]

#Preview Data
head(fatal)
```

# Fit Linear Regression Model

```{r,eval=FALSE}
#Fit Linear Regression Model
mod = lm(,data=fatal)

#Summary from Model
summary(mod)

#Pulling Out R-squared Adjusted R-squared
sum.out = summary(mod)

sum.out$r.squared

#Calculate R-squared by hand

```

**Interpretation of t-Tests:** Only predictor variable where we don't have enough evidence to conclude that it's coefficient/slope is significantly different from 0 is  *year*.

**Interpretation of Slope for *miles*:** Holding all other predictor variables (*youngdrivers, year, unemp*, and *beertax*) constant, the average number of vehicle fatalities per 1000 people in a state will increase by 0.0000015960 for every 1 unit increase in the average miles per driver in that state. 

**Alternative Interpretation of Slope for *miles*:** Holding all other predictor variables (*youngdrivers, year, unemp*, and *beertax*) constant, the average number of vehicle fatalities per 1000 people in a state will increase by 0.0015960 if the average miles per driver in that state increased by 1,000. 

# Difference Between R-squared and Adjusted R-squared

```{r,eval=TRUE}
mod.without.year = lm(adj_fatal~youngdrivers + unemp + beertax + miles,data=fatal)
mod.with.year = lm(adj_fatal~youngdrivers + year + unemp + beertax + miles,data=fatal)

#Compare R-squared (Increases)
summary(mod.without.year)$r.squared - summary(mod.with.year)$r.squared


#Compare adjusted R-squared (Increases by Slightly Less)
summary(mod.without.year)$adj.r.squared - summary(mod.with.year)$adj.r.squared

```

# ANOVA Table

```{r,eval=FALSE}

#Run anova() function and notice how it is broken down by predictor variable. This is called sequential sum of squares.
#P-value in F-Test is Actually Testing if the Previous Model is significantly different than the Previous Model with the variable added. 

anova(mod)

#Modified ANOVA function (anova455)


#Another Option for Getting F-statistic
mod.none=lm(,data=fatal) #Intercept Only
mod.full=lm(, data=fatal) #Full Model Includes Intercept

#Table has all the same information but is presented differently.
anova(mod.none,mod.full)

```

#Confidence Intervals and Prediction Intervals

```{r,eval=FALSE}
#Remove non-significant variable year
mod.final = lm(,data=fatal)
summary(mod.final)

#Set Values of Predictor Variables to Predict Y at
youngdrivers = 
unemp = 
beertax = 
miles = 

predict(mod,newdata=data.frame(youngdrivers,unemp,beertax,miles),interval="confidence")

predict(mod,newdata=data.frame(youngdrivers,unemp,beertax,miles),interval="prediction")
```

