---
title: "Class 1 R Notebook"
output:
  pdf_document: default
  html_notebook: default
---

```{r, echo=F}
# Put all Required Packages Here
library(readr)
```

# Read in Dataset

```{r}
# loads a package needed to use the read_csv() function
# install package before first using it for the first time

lego <- read_csv("lego.csv")

# Alternative way to load lego (remove # to use)
# You can load a csv file directly from internet (i.e. Github)
# lego <- read_csv("https://raw.githubusercontent.com/JA-McLean/STOR455/master/data/lego.csv")
```

# Preview Dataset

```{r}
head(lego) #Vertically (Top 6 Rows by Default)
str(lego)  #Horizontally
```

# Summary of Amazon Price

### Numerically

```{r}
#dataframe$variable

mean(lego$Amazon_Price,na.rm=T)
median(lego$Amazon_Price,na.rm=T)
sd(lego$Amazon_Price, na.rm=T)
```

### Visually

Example of how to add a summary to R Code. You can write paragraphs outside the code chunks like this. For example, I may want to tell my audience that the visual below shows a histogram and boxplot of the Amazon price of lego sets, and we can clearly see that the distribution is extremely right-skewed.

```{r}
hist(lego$Amazon_Price, breaks=100) #Use Help to Find Out How to Change # of Bins
boxplot(lego$Amazon_Price)
```


# Creating Objects and Doing Calculations

```{r}
# Assignment operators in R: = vs. <-
# Notice Global Environment



```





