---
title: "Supplement for Lecture 10: Partitioning Variability"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
#This code chunk is for modifying the global options and for loading required R packages
knitr::opts_chunk$set(echo = TRUE)
options(scipen=999) #Prevents the use of scientific notation
library(rmarkdown)
library(tinytex)
library(knitr)
library(readr)
library(mosaic) #Install Mosaic Package
library(AER)
```

# Load Data 

```{r, message=FALSE}
data("Fatalities") # Load Data

fatal = Fatalities[,c("fatal","pop","youngdrivers")]

head(fatal)
```

Variables of Interest
- *fatal* = Number of vehicle fatalities
- *pop* = Population
- *youngdrivers* = Percent of Drivers 15 - 24

# Create New Variable to Adjust for Population

```{r,fig.width=4,fig.height=3,eval=TRUE}
#Consider scatterplot
plot(x=fatal$pop,y=fatal$fatal)

#Create New Variable Called adj_fatal
fatal$adj_fatal = (fatal$fatal/fatal$pop)*1000

#Remove Original Variable
fatal$fatal = NULL

#Preview Modified Dataset
head(fatal)

#Consider new scatterplot
plot(x=fatal$pop,y=fatal$adj_fatal)
```

# Output from Simple Linear Regression

```{r,eval=FALSE}
#Model for the relationship between fatalities and proportion of young drivers.

mod = lm(adj_fatal~youngdrivers,data=fatal)
summary(mod)

#Create new variable for youngdrivers to help interpretation of slope


#Manually calculate p-value using the t-distribution
   #Find area to right and multiply by 2

#We have found significance. Hooray!!. Let's visualize the model.


```

Focus on the "t value" and "Pr(>|t|)". These are your test statistics and p-values for testing the following hypotheses:

$$H_0:\beta_x=0$$
$$H_a:\beta_x\neq 0$$
In class, we focused on when $x=1$. But we could do the same test for the intercept when $x=0$.


# Confidence Interval for the Slope (and Intercept)

```{r,eval=FALSE}

```

**Interpretation of the confidence interal:** I am 95 percent confident, that the (average/expected/predicted) number of vehicle fatalities (per 1000) will increase by a number between BLANK1 and BLANK2 for every 1 percent increase in the percent of young drivers.

# ANOVA

```{r,eval=FALSE}


#Manually find the p-value and check it matches
   #Want the area to the right of 19.422
```
Notice how the p-value for the F-test is identical to the p-value from the t-test. Notice how this p-value is in the output for `summary()`. Also, the last row for the *Total* is not there.

```{r,eval=FALSE}
#Hand Calculation of SST

#Notice that this equals the sum from the ANOVA table
0.0598+1.02930
```



