---
title: "Supplement for Lecture 7: Outliers and Influential Points"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
#This code chunk is for modifying the global options and for loading required R packages
knitr::opts_chunk$set(echo = TRUE)
library(rmarkdown)
library(tinytex)
library(knitr)
library(readr)
library(mosaic) #Install Mosaic Package
library(Stat2Data) #Install Stat2Data
```

# Load Data from Textbook

```{r, message=FALSE}
data("SpeciesArea") # Load Data

species = SpeciesArea[,-c(4,5)] # Shorten Name and Remove Last 2 Columns

rm(SpeciesArea) #Removes Old Object from Environment

head(species)
```

# Linear Model for Species vs Area

```{r,out.width="50%"}
SpeciesModel=lm(Species~Area, data=species)

plot(Species ~ Area,data=species,pch=16,col="blue")
abline(SpeciesModel)

plot(SpeciesModel$residuals~SpeciesModel$fitted.values,pch=16,col="blue")
abline(0,0)
```

# Default Plots from lm Object

```{r,out.width="50%"}
plot(SpeciesModel) #Default Argument which=c(1,2,3,5)

#See ?plot.lm (6 Plots Available)

#Plot 1: Residuals vs Fitted (We Did This Already)
#Plot 2: Normal QQ (We Did This Already)
#Plot 3: Square Root of Absolute Standardized Residual vs Fitted (Check for Outliers)
#Plot 4: Not Part of Default
#Plot 5: Residuals vs Leverage (Check for Influence)
#Plot 6: Not Part of Default

plot(SpeciesModel, which=c(1,2)) #Only Want First Two

```
# Identifying Outliers

```{r,out.width="50%"}
#Alternate to SpeciesModel$residuals
residuals(SpeciesModel)

max(residuals(SpeciesModel)) #Largest
min(residuals(SpeciesModel)) #Smallest
max(abs(residuals(SpeciesModel))) #Farthest Away from 0

which.max(abs(residuals(SpeciesModel))) #Returns Index of the Max

#Bad Idea: Remove Data Point with Largest Outlier
species.without.3 = species
species.without.3

#Standardizing Residuals
SSE=sum(residuals(SpeciesModel)^2)
n=length(residuals(SpeciesModel))
std.error.regression = sqrt(SSE/(n-2))
std.error.regression #Expect to be Off By 15 Species On Average When Using Model to Predict
summary(SpeciesModel)

#Plot of Standardized Residuals
std.res=residuals(SpeciesModel)/std.error.regression
plot(y=std.res,x=fitted(SpeciesModel),
     main="Standardized Residuals Versus Fitted Values",
     xlab="Fitted Values", ylab="Standardized Residuals",
     ylim=c(-2.5,2.5))
abline(h=c(-2,2),
       col="red",
       lty=c(2,2),
       lwd=c(3,3))
```

# Assess Conditions of Residuals

```{r,out.width="50%"}
qqnorm(SpeciesModel$residuals)
qqline(SpeciesModel$residuals)
hist(SpeciesModel$residuals)
```

# Transformation

Three Possible Options Using Natural Logarithm Transformation Only

- $y=\beta_0 +\beta_1log(x) + \epsilon$
- $log(y)=\beta_0 +\beta_1x + \epsilon$
- $log(y)=\beta_0 +\beta_1log(x) + \epsilon$

```{r,out.width="50%"}
# Run the Code and Try All Three To Choose Best
TransMod=lm(Species~log(Area), data=species)
summary(TransMod)

plot(Species ~ log(Area),data=species,pch=16,col="blue")
abline(TransMod)
#abline(v=c(5,12),col=c("red","red"),lwd=c(3,3),lty=c(3,3)) #Run for First Option

plot(TransMod,c(1,2))
```
# Getting Fitted Values, Residuals, and Predictions

Using the model we fit to make predictions:

$$ \widehat{\log(y)} = \hat\beta_0 + \hat\beta_1 \log(x) $$

Transforming predictions back to the units of $Y=\textrm{Number of Species}$

$$\hat{y}=e^{\widehat{\log(y)}}=e^{\hat\beta_0 + \hat\beta_1 log(x)}=e^{\hat\beta_0}x^{\hat\beta_1 } $$

If we run `coef(TransMod)`, we find our estimates

$$\hat{y}=e^{1.6249 + 0.2355 \log(x)}=e^{1.6249}x^{0.2355}$$

```{r,out.width="50%"}
#Recall Property of Logs
10^log10(5)
exp(log(7))

#Extract Coefficients
as.numeric(coef(TransMod))
beta0=as.numeric(coef(TransMod))[1]
beta1=as.numeric(coef(TransMod))[2]

#Raw Predictions of Log(Species)
species$logfit = fitted(TransMod)

#3 Methods for Predictions of Actual Species
species$fit1 = exp(species$logfit) 
species$fit2= exp(beta0+beta1*log(species$Area))
species$fit3 = exp(beta0)*species$Area^beta1

#Obtain Residuals in Original Units of Species Variable to Calculate SE of Regression
species$res = species$Species - species$fit1
sqrt(sum(species$res^2)/(length(species$res)-2)) #Standard Error of Regression

#Plot Fitted Model on Raw Untransformed Data
plot(Species~Area, data=species)

#Extrapolate for the Island Australia (7,700,000 km^2)
plot(Species~Area, data=species)
curve(exp(beta0+beta1*log(x)), add=TRUE, col="red")
```

