---
title: "Supplement for Lecture 2: Four Step Process"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
#This code chunk is for modifying the global options and for loading required R packages
knitr::opts_chunk$set(echo = TRUE)

#install.packages("rmarkdown")
library(rmarkdown)
library(tinytex)
library(knitr)
library(readr)
```

# Read in Dataset

```{r}
# Loads a package needed to use the read_csv() function
# CSV file needs to be in the same folder as your RMD file
# Default working directory is same as directory of your RMD file

lego1 <- read_csv("lego.csv")

# You can specify the full path on your computer like below
#lego2 = read_csv("D:/Mario Documents/UNC/STOR 455/STOR455_WEBSITE/Supplement/Model Basics/lego.csv")

# Created Objects lego1 and lego2 using <- and =
```

Notice that objects `lego1` and `lego2` have been added to the Global Environment. 

# Preview Dataset

```{r}
head(lego1) #Vertically (Top 6 Rows by Default)
str(lego1)  #Horizontally
names(lego1) #Get Vector of Variable Names
```

How would you show the top 12 rows instead of the top 6? You can use `?head` to access the documentation for the `head()` function.

# Subsetting the Data

### Datasets are Just Fancy Matrices

```{r}
dim(lego1)
```

This dataset has 1,304 observations or cases and 15 variables or covariates. The variables $n$ and $p$ are typically used to represent the sample size and number of variables. Therefore we would say that $n=1304$ and $p=15$. To subset the dataset we can use the double brackets to select/deselect rows or columns

```{r}
lego1[c(1,5, 10, 15, 20),]
lego1[,c(1,5, 15)]
lego1[,c("Item_Number","Price","Size")]
lego1[,names(lego1)[c(1,5,15)]]
```


### Subsetting Based Off Values

```{r}
hist(lego1$Pieces)

lego1$Pieces>1000

large_lego = lego1[lego1$Pieces>2000,]

small_lego = lego1[lego1$Pieces< 15,]

middle_lego=lego1[lego1$Pieces>15 & lego1$Pieces<2000,]

extreme_lego=lego1[lego1$Pieces<15 & lego1$Pieces>2000,]
```


# Mathematical/Statistical Functions

### Mathematical Calculations

```{r}
#Scalars
a=3
b=4

a+b
a-b
a*b
a/b
a^2
log(a) #Defaults to natural log
exp(a) # e^a


#Vectors
a=c(1,2,3,4)
b=c(2,3,4,5)

a+b
a-b
a*b
a/b
a^2
log(a)
exp(a)

#Combination (Based off Exercise 0.15: Roller Coasters)
yint=54
slope=7.6
TypeCode=c(0,1) #0=Wooden & 1=Steel

TopSpeed = yint+slope*TypeCode
TopSpeed
```

### Statistical Functions

```{r}
mean(lego1$Amazon_Price,na.rm=T)
median(lego1$Amazon_Price,na.rm=T)

sd(lego1$Amazon_Price,na.rm=T)
var(lego1$Amazon_Price,na.rm=T)
IQR(lego1$Amazon_Price,na.rm=T)

quantile(lego1$Amazon_Price,na.rm=T)
quantile(lego1$Amazon_Price,c(0.05,0.1,0.9,0.95),na.rm=T)

unique(lego1$Theme)
table(lego1$Theme)

table(lego1$Size,lego1$Availability)

na_rm_lego1 = na.omit(lego1)
cor(na_rm_lego1$Amazon_Price,na_rm_lego1$Price)
lm(Amazon_Price ~ Price, data=na_rm_lego1)
```